The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-11-17 paper/discussion.tex
add footnote addressing planet radius scaling Q

\paragraph{Precise features of the radius valley}
\begin{figure}[!tb]
    \centering
    \includegraphics[width=.6\textwidth]{figures/rate_density_vs_radius_model_4_xcut.pdf}
    \caption{
        Inferred planet occurrence rates as a function of planet radius in 
        a model with a radius gap (Eq.~\ref{eq:model4_radius_distribution}).
        Similar to Model \#3, this model has fixed primaries and single stars, 
        but varying secondaries.
    }
    \label{fig:model_4}
\end{figure}
Using improved stellar parameters measured by the California-{\it Kepler} 
survey,~\citet{fulton_california-_2017} recently reported a ``gap'' in 
the radius-period 
plane~\citep{petigura_california-kepler_2017,johnson_california-kepler_2017}.
The existence of the gap has been independently corroborated using 
asteroseismically-determined stellar 
parameters~\citep{van_eylen_asteroseismic_2017}.
Precise measurement of the gap's features, in particular its width, 
depth, and shape, requires accurate occurrence rates.
To illustrate binarity's role in the issue, we make identical assumptions as 
in Model \#3, but instead assume an intrinsic radius distribution
\begin{align}
p_r(r)
&\propto
\left.
\begin{cases}
r^\delta & \text{for } r\geq 2r_\oplus, \\
0 & \text{for } 1.5r_\oplus < r < 2r_\oplus, \\
{\rm constant} & \text{for } r\leq1.5r_\oplus.
\end{cases}
\right.
\label{eq:model4_radius_distribution}
\end{align}
The resulting true and inferred rates are shown in Fig.~\ref{fig:model_4}.
If left uncorrected, binarity makes the gap more shallow, and flattens 
the step-function edges.
At present though, binarity seems less important than other effects that would 
``blur'' the gap in the planet radius dimension. 
In particular, the valley's period-dependence is almost certainly not flat
\citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.
This means that any study assessing its width, depth, etc. only in the planet 
radius dimension must first account for the blurring that comes from 
marginalizing over the periods.

>>>>

\paragraph{Precise features of the radius valley}
\begin{figure}[!tb]
    \centering
    \includegraphics[width=.6\textwidth]{figures/rate_density_vs_radius_model_4_xcut.pdf}
    \caption{
        Inferred planet occurrence rates as a function of planet radius in 
        a model with a radius gap (Eq.~\ref{eq:model4_radius_distribution}).
        Similar to Model \#3, this model has fixed primaries and single stars, 
        but varying secondaries.
    }
    \label{fig:model_4}
\end{figure}
Using improved stellar parameters measured by the California-{\it Kepler} 
survey,~\citet{fulton_california-_2017} recently reported a ``gap'' in 
the radius-period 
plane~\citep{petigura_california-kepler_2017,johnson_california-kepler_2017}.
The existence of the gap has been independently corroborated from a sample of 
KOIs with asteroseismically-determined stellar 
parameters~\citep{van_eylen_asteroseismic_2017}.
Precise measurement of the gap's features, in particular its width, 
depth, and shape, will require more accurate occurrence rates.
To illustrate binarity's role in the issue, we make identical assumptions as 
in Model \#3, but instead assume an intrinsic radius distribution
\begin{align}
p_r(r)
&\propto
\left.
\begin{cases}
r^\delta & \text{for } r\geq 2r_\oplus, \\
0 & \text{for } 1.5r_\oplus < r < 2r_\oplus, \\
{\rm constant} & \text{for } r\leq1.5r_\oplus.
\end{cases}
\right.
\label{eq:model4_radius_distribution}
\end{align}
The resulting true and inferred rates are shown in Fig.~\ref{fig:model_4}.
If left uncorrected, binarity makes the gap appear more shallow, and flattens 
the step-function edges.
At present though, binarity seems less important than other effects that would 
``blur'' the gap in the planet radius dimension. 
In particular, the valley's period-dependence is almost certainly not flat
\citep{van_eylen_asteroseismic_2017,owen_evaporation_2017}.
This means that any study assessing its width, depth, etc. only in the planet 
radius dimension must first account for the blurring that comes from 
marginalizing over the periods.

### 2017-11-17 paper/model_3.tex
add footnote addressing planet radius scaling Q

For this model, we forgo analytic development and simply run our Monte Carlo 
program.
The resulting occurrence rates are shown in 
Fig.~\ref{fig:errcases_model_3_log}.
For the assumed planetary and stellar distributions, the inferred rate is 
underestimated over all radii.

>>>>

For this model, we forgo analytic development and simply run our Monte Carlo 
program\footnote{
One might worry that our Monte Carlo program does not increase the number of 
selected stars as the square of the planet radius (Eq.~\ref{eq:snr_true}).
We can omit this dependence because in our model $N_1/N_0$ is independent of 
desired planet radius, and all other terms in the rate densities ({\it e.g.}, 
Eqs.~\ref{eq:model2_rate_density} and~\ref{eq:model2_Gamma_a}) are independent 
of the number of selected stars.
}.
The resulting occurrence rates are shown in 
Fig.~\ref{fig:errcases_model_3_log}.
For the assumed planetary and stellar distributions, the inferred rate is 
underestimated over all radii.
